Synthesizing by means of mice

### 2021-09-21 mice_synthesizing/Mice_Synthesizing.Rmd
Adjust for apart simulations folder.
update
no idea what exactly. But let's get it up to a synced state

---
title: "Synthesizing by means of mice"
author:
- Thom Volker
- Utrecht University
date: "`r format(Sys.time(), '%d-%m-%Y')`"
output: 
  html_document:
    theme: spacelab
    highlight: tango
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
bibliography: federated_imp.bib
csl: "/Users/thomvolker/Documents/styles/apa-6th-edition.csl"
---

@@

```{r, include = F, cache = thomcache, cache.lazy=thomlazy}
source("1.a Synthesize_Mice_Replace_All.R")
source("functions.R")
```

@@

```{r, code = readLines("functions.R")}
```

>>>>

---
title: "Synthesizing by means of mice"
author:
- Thom Volker
- Utrecht University
date: "`r format(Sys.time(), '%d-%m-%Y')`"
reveal_options:
      width: 100%
      height: 100%
      margin: 0.1
output: 
  html_document:
    theme: spacelab
    highlight: tango
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
bibliography: federated_imp.bib
csl: "/Users/thomvolker/Documents/styles/apa-6th-edition.csl"
---

@@

```{r, include = F, cache = thomcache, cache.lazy=thomlazy}
source("simulations/1.a Synthesize_Mice_Replace_All.R")
source("simulations/functions.R")
```

@@

```{r, code = readLines("simulations/functions.R")}
```
